Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-25 article.tex
discussion finished

% Needed references are currently highlighted as TODO:

@@

TODO: A literature review regarding this does here TODO:.

The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest/disease control, economic pressures, and climate conditions as key factors. Many of these singular relationships are well-defined within literature studies such as TODO:.

@@

The interpretation of results from the Bayesian Network models enhances our understanding of environmental sustainability in viticulture by providing a detailed and structured analysis of key factors and their interactions. The findings underscore the importance of integrated management practices that consider the interconnected nature of water quality, pest and disease management, market pressures, agrochemical use, and climate conditions. By aligning with and expanding upon existing literature, this study offers valuable insights for both researchers and practitioners aiming to promote sustainability in viticulture.

>>>>

@@

The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest/disease control, economic pressures, and climate conditions as key factors. Many of these singular relationships are well-defined within literature studies such as those between climate and pest/disease \cite{olatinwoChapterWeatherbasedPest2014}. Furthermore, literature  highlights a growing need for data and more decision support tools to assist with combatting external pressures such climate, water scarciy and disease \cite{naigeonDATADecisionmakingViticulture2023,stefaniniBayesianCausalModel2022,fincoCombiningPrecisionViticulture2022a,laurentLocalInfluenceClimate2022}. Tools such as Bayesian networks are becoming more applied to assist with the creation of decision support tools such as with water management \cite{carmonaUseParticipatoryObjectOriented2011} or vineyard placement \cite{abbalDecisionSupportSystem2016}. However, the combination of holistic approaches to reviewing sustainable practices in the adoption of techniques through measurable and holistic approaches is a growing need in policy creation and uptake of new novel sustainable practices \autocite{mayfieldDesigningExpertledBayesian2023,baianoOverviewSustainabilityWine2021,dichiaraCollaborativeApproachAchieving2024}. Although more holistic approaches are required to review the total accumulated benefits of sustainable practices, it is well aligned between researchers, the public and policy-makers that this endeavour is of great importance to the Australian agricultural industry as a whole \cite{dumbrellComparingAustralianPublic2024}.

@@
